Detecting changes in dispersion in COVID-19 incidence time series using a negative binomial model

### 2024-12-06 manuscript/ms (2).tex
Update incidence equations

We model broad-scale change in incidence as $log(E[I_t / N])  = \sum_j \beta_j h_j(t)$. A persistent challenge in investigating changes in variability has been ``spurious correlation'' with population size. 
Since population size influences the mean and variance of case count data and thus could have an impact on estimates of dispersion, we adjust for population size using an offset in the model. 
There is an offset term in order to directly model counts (here, COVID-19 cases) per unit of observation (here, per individual). Let $I_i$ be the number of infections at time step i and $h_i$

\begin{align}
  \log(E[I]/N) &= \beta_1h_1(t_i) + \beta_2h_2(t_i) + \beta_3h_3(t_i) \\
  \log(E[I])-\log(N) &= \beta_1h_1(t_i) + \beta_2h_2(t_i) + \beta_3h_3(t_i) \\ 
  \log(E[I_i]) &= \beta_1 h_1(t_i) + \beta_2h_2(t_i) + \beta_3 h_3(t_i) + log(n_i) 
\end{align}

>>>>

We model broad-scale change in incidence as 
\begin{equation}
  \log(E[I_t / N])  = \sum_j \beta_j h_j(t)
\end{equation}
A persistent challenge in investigating changes in incidence dispersion the statistical impact of population size on dispersion. 
Since population size influences the mean and variance of case count data it impacts estimates of dispersion even in populations that are otherwise identical.
Accordingly, population size appears as an offset in our model of broad-scale incidence changes.
Letting $I_t$ be the number of infections at time $t$ in a population of size $N$, equation (x) implies
\begin{equation}
  \log(E[I_t]) &= \sum_j \beta_j h_j(t) + \log(N) 
\end{equation}
